Conversations in time: interactive visualization to explore structured temporal data

### 2020-08-07 tsibbletalk.Rmd
rewrote tsibble data

The \CRANpkg{tsibble} package extends the `data.frame` and \CRANpkg{tibble} structure to represent temporal data in tidy format [cite]. A tsibble consists of *index*, *key*, and other measured variables in one data frame. The *index* column holds time-based indices. The *key* column(s) uniquely identifies a collection of related observational units during a period of time defined by *index*. They are "sticky" columns to a `tsibble` over the course of transformation.

>>>>

The \CRANpkg{tsibble} package [@wang2020tsibble] introduces a unified temporal data structure, referred to as a `tsibble`, to represent time series and longitudinal data in a tidy format [@wickham2014tidy]. That said, a `tsibble` extends the `data.frame` and \CRANpkg{tibble} class with temporally contextual metadata: `index` and `key`. The `index` declares a data column that holds time-related indices. The `key` identifies a collection of related series or panels observed over the `index`-defined period, which can contain multiple columns. Below displays the monthly Australian retail trade turnover data, available in the \CRANpkg{tsibbledata} package. The `Month` column holds year-months as `index`. The `State` together with `Industry` are the identifiers for these 152 series, highlighted as `key`. Note that the column `Series ID` could be an alternative option for setting up `key`, but `State` and `Industry` are informative. The `index` and `key` are "sticky" columns to a `tsibble`, forming critical pieces for fluent temporal data analysis later.

```{r, aus-retail}
library(tsibble)
library(tsibbledata)
print(aus_retail, n = 5)
```

### 2020-08-07 tsibbletalk.tex
rewrote tsibble data

The \CRANpkg{tsibble} package extends the \texttt{data.frame} and
\CRANpkg{tibble} structure to represent temporal data in tidy format
{[}cite{]}. A tsibble consists of \emph{index}, \emph{key}, and other
measured variables in one data frame. The \emph{index} column holds
time-based indices. The \emph{key} column(s) uniquely identifies a
collection of related observational units during a period of time
defined by \emph{index}. They are ``sticky'' columns to a
\texttt{tsibble} over the course of transformation.

>>>>

The \CRANpkg{tsibble} package \citep{wang2020tsibble} introduces a
unified temporal data structure, referred to as a \texttt{tsibble}, to
represent time series and longitudinal data in a tidy format
\citep{wickham2014tidy}. That said, a \texttt{tsibble} extends the
\texttt{data.frame} and \CRANpkg{tibble} class with temporally
contextual metadata: \texttt{index} and \texttt{key}. The \texttt{index}
declares a data column that holds time-related indices. The \texttt{key}
identifies a collection of related series or panels observed over the
\texttt{index}-defined period, which can contain multiple columns. Below
displays the monthly Australian retail trade turnover data, available in
the \CRANpkg{tsibbledata} package. The \texttt{Month} column holds
year-months as \texttt{index}. The \texttt{State} together with
\texttt{Industry} are the identifiers for these 152 series, highlighted
as \texttt{key}. Note that the column \texttt{Series\ ID} could be an
alternative option for setting up \texttt{key}, but \texttt{State} and
\texttt{Industry} are informative. The \texttt{index} and \texttt{key}
are ``sticky'' columns to a \texttt{tsibble}, forming critical pieces
for fluent temporal data analysis.

\begin{Schunk}
\begin{Soutput}
#> # A tsibble: 64,532 x 5 [1M]
#> # Key:       State, Industry [152]
#>   State                Industry                    `Series ID`    Month Turnover
#>   <chr>                <chr>                       <chr>          <mth>    <dbl>
#> 1 Australian Capital ~ Cafes, restaurants and cat~ A3349849A   1982 Apr      4.4
#> 2 Australian Capital ~ Cafes, restaurants and cat~ A3349849A   1982 May      3.4
#> 3 Australian Capital ~ Cafes, restaurants and cat~ A3349849A   1982 Jun      3.6
#> 4 Australian Capital ~ Cafes, restaurants and cat~ A3349849A   1982 Jul      4  
#> 5 Australian Capital ~ Cafes, restaurants and cat~ A3349849A   1982 Aug      3.6
#> # ... with 64,527 more rows
\end{Soutput}
\end{Schunk}
